Computer Science House Constitution

### 2025-06-09 constitution.tex

\asubsection{Semantic Changes}
\asubsubsection{Amendments}
Any semantic change to the Constitution requires the change to be proposed in writing for discussion at a House Meeting.
Any modifications made due to the discussion are added to the written proposal and the modified proposal is posted during the week.
The final proposal is presented the following week, and ballots are distributed for a Balloted Two-Thirds Vote with two-thirds quorum as described in \ref{Balloted Vote}.
The ballots are collected for a minimum of a forty-eight hour period.
A quorum of two-thirds of Eligible Votes must cast ballots for the vote to be official.
A vote equaling or exceeding two-thirds of the number of Votes Cast is required for the change to be placed into the Constitution.
\asubsubsection{Compliance with RIT Policy and New York State Law}
Any change made to Article  \ref{ADHERENCE TO UNIVERSITY POLICIES} which is made due to an update in NY law or RIT policy may be treated as a Non-Semantic change.

@@

\asubsection{Selection of a Root Type Person}
\renewcommand{\theenumi}{\alph{enumi}} % For this section, we want items to use letters
\begin{enumerate}
	\item Nominations are taken from the RTPs meeting the selection criteria in \ref{Qualifications of a Root Type Person}.
	\item Each candidate is given a minimum of twenty-four hour period to accept or decline the nomination.
	\item A list of all nominees who have accepted is presented to E-Board for approval.
	      This E-Board Meeting is closed to E-Board Members, RTPs, and members with explicit invitation from E-Board.
	\item If an E-Board Member is a candidate for the office in discussion, the member is absent and their vote is abstained.
	      An E-Board Vote, as described in \ref{Executive Board Vote}, is taken to determine whether the nominations of the RTP(s) are accepted.
\end{enumerate}

>>>>

\asubsection{Semantic Changes}
\asubsubsection{Amendments}
Any semantic change to the Constitution requires the change to be proposed in writing for discussion at a House Meeting.
Any modifications made due to the discussion are added to the written proposal and the modified proposal is posted during the week.
The final proposal is presented the following week, and ballots are distributed for a Balloted Two-Thirds Vote with two-thirds quorum as described in \ref{Balloted Vote}.
The ballots are collected for a minimum of forty-eight hours.
A quorum of two-thirds of Eligible Votes must cast ballots for the vote to be official.
A vote equaling or exceeding two-thirds of the number of Votes Cast is required for the change to be placed into the Constitution.
\asubsubsection{Compliance with RIT Policy and New York State Law}
Any change made to Article  \ref{ADHERENCE TO UNIVERSITY POLICIES} which is made due to an update in NY law or RIT policy may be treated as a Non-Semantic change.

@@

\asubsection{Selection of a Root Type Person}
\renewcommand{\theenumi}{\alph{enumi}} % For this section, we want items to use letters
\begin{enumerate}
	\item Nominations are taken from the RTPs meeting the selection criteria in \ref{Qualifications of a Root Type Person}.
	\item Each candidate is given a minimum of twenty-four hours to accept or decline the nomination.
	\item A list of all nominees who have accepted is presented to E-Board for approval.
	      This E-Board Meeting is closed to E-Board Members, RTPs, and members with explicit invitation from E-Board.
	\item If an E-Board Member is a candidate for the office in discussion, the member is absent and their vote is abstained.
	      An E-Board Vote, as described in \ref{Executive Board Vote}, is taken to determine whether the nominations of the RTP(s) are accepted.
\end{enumerate}
